---
title: "Emmys"
output: github_document
---


```{r setup, include = FALSE}
library(tidytuesdayR)
library(tidyverse)
library(lubridate)
library(purrr)
library(rlang)
library(fs)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "80%",
  fig.align = "center"
)
```

```{r}
library(tidytuesdayR)
library(tidyverse)
library(lubridate)
library(purrr)
library(rlang)
library(fs)
```

Download and save data into *rds* files.

```{r}
if(length(dir_ls(glob = "*.rds")) == 0) {
  imap(
    tt_load("2021-09-21"), 
    ~ write_rds(.x, path(.y, ext = "rds"))
  )}
```

Checking out the data set

```{r}
data_nominees <- read_rds("nominees.rds")

glimpse(data_nominees)
```

Cursory plotting of the data revealed a data issue.  The number of nominees jump in 2,000's.  There another dip on 2,014.

```{r}
data_nominees %>% 
  count(year) %>% 
  ggplot(aes(year, n)) +
  geom_col()
```
A quick count shows that we should use the data from 2,015 and after.

```{r}
data_nominees %>% 
  count(year) %>% 
  arrange(-year) %>% 
  head(20)
```

Plotting the top 5 winning Distributors.  VH1 suddenly appears as a contender on 2,021

```{r}
data_nominees %>% 
  filter(year >= 2015, type == "Winner") %>% 
  count(year, distributor) %>% 
  arrange(year, -n) %>% 
  group_by(year) %>% 
  mutate(rn = row_number()) %>% 
  filter(rn <= 4) %>% 
  ungroup() %>% 
  ggplot() +
  geom_col(aes(year, n, fill = distributor)) +
  theme(legend.position = "bottom")
```
Pulling up the data for VH1 shows that there is an entry per Producer, thus inflating the number of "wins" that needs to be deduped.

```{r}
data_nominees %>% 
  filter(year >= 2015, type == "Winner", distributor == "VH1") %>% 
  select(category, title, production, year)
```

```{r}
prep_winners <- data_nominees %>% 
  filter(year >= 2015, type == "Winner") %>% 
  mutate(
    category = str_sub(category, 1, nchar(category) - 7),
    category = str_to_title(category)
    ) %>% 
  group_by(category, title, year, distributor) %>% 
  summarise(.groups = "drop") %>% 
  ungroup() %>% 
  arrange(category, title, year, distributor)

glimpse(prep_winners)
```

```{r}
prep_winners %>% 
  count(year)
```


```{r}
dist_winners <- prep_winners %>% 
  count(year, distributor, sort = TRUE) %>% 
  ungroup() %>% 
  arrange(year, -n) %>% 
  group_by(year) %>% 
  mutate(
    top = ifelse(row_number() <= 3, TRUE, FALSE),
    distributor = ifelse(top, distributor, "Other")
    ) %>% 
  group_by(year, distributor) %>% 
  summarise(wins = sum(n), .groups = "drop")

dist_winners %>% 
  ggplot() +
  geom_col(aes(year, wins, fill = distributor))
```

```{r}
prep_winners %>% 
  filter(year == 2015, distributor == "Comedy Central") %>% 
  count(title, sort = TRUE)
```

```{r}
prep_winners %>% 
  filter(year == 2020, distributor == "Pop TV") %>% 
  count(title, sort = TRUE)
```
```{r}
prep_winners %>% 
  filter(year == 2016, distributor == "FX Networks") %>% 
  count(title, sort = TRUE)
```

```{r}
prep_winners %>% 
  filter(year == 2019, distributor == "Prime Video") %>% 
  count(title, sort = TRUE)
```
```{r}
prep_winners %>% 
  filter( distributor == "NBC") %>% 
  count(year, title, sort = TRUE) %>% 
  pivot_wider(names_from = "year", values_from = "n")
```
```{r}
order_dist <- dist_winners %>% 
  count(distributor) %>% 
  arrange(n) %>% 
  pull(distributor)

order_dist
```

```{r}
prep_winners %>% 
  filter(year == 2021, distributor == "Disney+") %>% 
  count(title, sort = TRUE)
```


```{r}
prep_winners %>% 
  filter(title == "The Mandalorian") %>% 
  arrange(year)
```
```{r}
prep_winners %>% 
  filter(year == 2021, title == "The Crown") %>% 
  arrange(category)
```


```{r}
dist_winners %>% 
  #filter(distributor != "Other") %>% 
  mutate(distributor = fct_relevel(distributor, order_dist)) %>% 
  ggplot() +
  geom_col(aes(year, wins, fill = distributor), position = position_stack()) 
```




